Red-Giant Hot Jupiters: Brilliant Radio Beacons?

### 2015-07-24 ms.tex
note for additional discussion on time variability, cartoon replaced

@@

@@

(Jason?)

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[htbp]
   \plotoneh{cartoon.pdf}
   \caption{A cartoon of radio emission spectra of a Jovian-mass RGHJ and the host red giants with 100 $R_{\odot }$. The spectrum of RGHJ is modeled after Jovian radio spectra \citep[][e.g.]{zarka2004}, while that of the host red giant is obtained simply by extrapolating observed radio spectra above 1~GHz with power law. }
  \label{fig:cartoon}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[htbp]
   \plotoneh{cartoon2.pdf}
   \caption{A cartoon of radio emission spectra of a Jovian-mass RGHJ and the host red giants with 100 $R_{\odot }$. The spectrum of RGHJ is modeled after Jovian radio spectra \citep[][e.g.]{zarka2004}, while that of the host red giant is obtained simply by extrapolating observed radio spectra above 1~GHz with power law. }
  \label{fig:cartoon}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Radio Flux from Nearby Evolved Stars}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Discriminating from Background:\\Time Variability}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

(from short to long)
\begin{itemize}
\item Modulation due to planetary spin rotation (condition: misalignment of spin axis and magnetic axis) 
\item modulation due to the presence of satellites??
\item Modulation due to orbital motion of the planet (condition: near edge-on orbit)
\item Variability of stellar wind due to stellar oscillation 
\end{itemize}

@@
